European or American? A re-examination of the transatlantic influence over the IMF

### 2025-10-04 manuscript/manuscript.qmd
manuscript: fix 2nd chunk name

```{r percentage_variance}
load('save/PCA.RData')
US_PC1_percentage <- US$sdev[1]^2 / sum(US$sdev^2) * 100
EU_PC1_percentage <- EU$sdev[1]^2 / sum(EU$sdev^2) * 100
```

>>>>

```{r}
#| label: percentage_variance
load('save/PCA.RData')
US_PC1_percentage <- US$sdev[1]^2 / sum(US$sdev^2) * 100
EU_PC1_percentage <- EU$sdev[1]^2 / sum(EU$sdev^2) * 100
```
